---
title: "Empirical Bayes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Empirical Bayes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \newcommand{\R}{\mathbb{R}}
  \newcommand{\B}{\boldsymbol\beta}
  \newcommand{\hb}{\boldsymbol{\hat\beta}}
  \newcommand{\E}{\boldsymbol\epsilon}
  \DeclareMathOperator*{\argmin}{argmin}
  \DeclareMathOperator*{\argmax}{argmax}
  \newcommand{\defn}{\mathpunct{:}=}
  \newcommand{\X}{\mathbf{X}}
  \newcommand{\Y}{\mathbf{Y}}
  \newcommand{\by}{\mathbf{y}}
  \newcommand{\bz}{\mathbf{Z}}
  \newcommand{\ba}{\boldsymbol{\alpha}}
  \newcommand{\bc}{\mathbf{c}}
  \newcommand{\bu}{\mathbf{u}}
  \def\Cov{\mathrm{Cov}}
  \def\Var{\mathrm{Var}}
  \def\Corr{\mathrm{Corr}}
  \def\vec{\mathrm{vec}}
---

```{r rmdsetup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "70%",
  fig.align = "center",
  fig.width = 6,
  fig.asp = .618
)
options(digits = 3)
set.seed(1)
```

```{r setup}
library(bvhar)
```

# Hyperparameters in Normal-inverse-Wishart Priors

In this vignette, we discuss hyperparameters of Normal-inverse-Wishart priors for BVAR, BVHAR-S, and BVHAR-L.

## BVAR

From Litterman (1986) and Bańbura et al. (2010), there are $\sigma_j$ (`sigma`), $\lambda$ (`lambda`), and $\delta_j$ (`delta`) in BVAR.

- $\sigma_i^2 / \sigma_j^2$ in Minnesota moments explain the data scales.
- $\delta_j$'s are related to the belief to random walk.
    - If $\forall j \; \delta_j = 1$, it is random walk prior (Litterman (1986) setting).
    - If $\forall j \; \delta_j = 0$, it is white noise.
- $\lambda$ controls the overall tightness of the prior around these two prior beliefs.

In addition, there is small number $\epsilon$ (`eps`) for matrix invertibility. This is set to be `1e-04` (default). You can change the number.
Based on these properties, users should *subjectively* choose hyperparameter.

Consider four indices of CBOE ETF volatility index (`etf_vix`):  *Gold, crude oil, emerging markets, gold miners, and silver*. We split train-test set (Test = last 20 points).

```{r datasub}
etf_split <- 
  etf_vix %>% 
  dplyr::select(GVZCLS, OVXCLS, VXEEMCLS, VXGDXCLS, VXSLVCLS) %>% 
  divide_ts(20)
# split---------------------
etf_train <- etf_split$train
etf_test <- etf_split$test
dim_data <- ncol(etf_train)
```

The following is BVAR Minnesota prior specification.

- `sigma`: standard error
- `lambda`: not that small number because small dimension
- `delta`: Litterman's setting

```{r bvarspec}
sig <- apply(etf_train, 2, sd)
lam <- .2
del <- rep(1, dim_data)
# bvharspec------------------
(bvar_spec <- set_bvar(
  sigma = sig,
  lambda = lam,
  delta = del,
  eps = 1e-04
))
```

There are one more parameter, order $p$. Set this $p = 3$.

```{r bvarinit}
bvar_cand <- bvar_minnesota(
  y = etf_train, 
  p = 3, 
  bayes_spec = bvar_spec, 
  include_mean = TRUE
)
```

## BVHAR-S

BVHAR-S (Kim et al. (n.d.)) has the same set of hyperparameters with BVAR.

```{r bvharsspec}
(bvhar_short_spec <- set_bvhar(
  sigma = sig,
  lambda = lam,
  delta = del,
  eps = 1e-04
))
```

```{r bvharsinit}
bvhar_short_cand <- bvhar_minnesota(
  y = etf_train, 
  har = c(5, 22), 
  bayes_spec = bvhar_short_spec, 
  include_mean = TRUE
)
```

## BVHAR-L

While above two priors set prior mean zero for farther coefficient (i.e. $A_2, \ldots, A_p$ or $\Phi^{(w)}, \Phi^{(m)}$), now these weekly and monthly coefficients are also have nonzero prior mean. So instead of $\delta_j$, there are

- $d_j$ for daily term.
- $w_j$ for weekly term.
- $m_j$ for monthly term.

```{r bvharlspec}
dayj <- rep(.8, dim_data)
weekj <- rep(.2, dim_data)
monthj <- rep(.1, dim_data)
# bvharspec------------------
bvhar_long_spec <- set_weight_bvhar(
  sigma = sig,
  lambda = lam,
  eps = 1e-04,
  daily = dayj,
  weekly = weekj,
  monthly = monthj
)
```

```{r bvharlinit}
bvhar_long_cand <- bvhar_minnesota(
  y = etf_train, 
  har = c(5, 22), 
  bayes_spec = bvhar_long_spec, 
  include_mean = TRUE
)
```


# Hyperparameter Selection

- Giannone et al. (2015) provides the closed form of marginal likelihood for BVAR Minnesota prior.
- Based on this calculation, Kim et al. (n.d.) gives the closed form for BVHAR-S and BVHAR-L.

This package provides hyperparameter selection function with empirical bayes (Giannone et al. (2015)).
Implementation is simple. Provide above `bvharspec` as initial values to `stats::optim()` structure. You can either use

- Individual `choose_bvar()` or `choose_bvhar()` function
- or one integrated `choose_bayes()` function

## Individual Functions

You can parallelize the computation with `optimParallel::optimParallel()` by specifying `parallel = list()` (if you leave it as empty list, the function execute `stats::optim()`). Register cluster, and pass `cl = cl`. For the details of other two, please see the documentation of the `optimParallel::optimParallel()`.

- `cl`: Register `cluster`
- `forward`: Recommendation - `FALSE`
- `loginfo`: Recommendation - `FALSE`

```{r parallelcl}
cl <- parallel::makeCluster(2)
```

### BVAR

We first try BVAR. `choose_bvar(bayes_spec, lower = .01, upper = 10, eps = 1e-04, y, p, include_mean = TRUE, parallel = list())` chooses BVAR hyperparameter. Observe that it fixes the order `p` (of course `eps`, either).

By default, it apply `.01` to lower bound and `10` to upper bound.
When using the function, setting lower and upper bounds can be quite tricky.
It's because the bound should be expressed by vector as in the `stats::optim()` function.
See the following code how to specify the bound.

```{r bvaroptim}
(bvar_optim <- choose_bvar(
  bayes_spec = bvar_spec,
  lower = c(
    rep(1, dim_data), # sigma
    1e-2, # lambda
    rep(1e-2, dim_data) # delta
  ),
  upper = c(
    rep(15, dim_data), # sigma
    Inf, # lambda
    rep(1, dim_data) # delta
  ),
  eps = 1e-04,
  y = etf_train,
  p = 3,
  include_mean = TRUE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

The result is a class named `bvharemp`.

```{r optimlist}
class(bvar_optim)
names(bvar_optim)
```

It has the chosen specification (`bvharspec`), fit (`bvarmn`), and its marginal likelihood value (`ml`).

```{r bvarchoose}
bvar_final <- bvar_optim$fit
```

### BVHAR-S

`choose_bvhar(bayes_spec, lower = .01, upper = 10, eps = 1e-04, y, har = c(5, 22), include_mean = TRUE, parallel = list())` choses hyperparameter set of BVHAR-S or BVHAR-L given `bayes_spec`.
If it is `set_bvhar()`, it performs BVHAR-S. It it is `set_weight_bvhar()`, it performs BVHAR-L.

```{r bvharsoptim}
(bvhar_short_optim <- choose_bvhar(
  bayes_spec = bvhar_short_spec,
  lower = c(
    rep(1, dim_data), # sigma
    1e-2, # lambda
    rep(1e-2, dim_data) # delta
  ),
  upper = c(
    rep(15, dim_data), # sigma
    Inf, # lambda
    rep(1, dim_data) # delta
  ),
  eps = 1e-04,
  y = etf_train,
  har = c(5, 22),
  include_mean = TRUE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

The structure of the result is the same.

```{r optimbvharslist}
class(bvhar_short_optim)
names(bvhar_short_optim)
```

```{r bvharschoose}
bvhar_short_final <- bvhar_short_optim$fit
```

### BVHAR-L

Using the same `choose_bvhar()` function, you should change `bayes_spec` and the length of bounds vectors:

```{r bvharloptim}
(bvhar_long_optim <- choose_bvhar(
  bayes_spec = bvhar_long_spec,
  lower = c(
    rep(1, dim_data), # sigma
    1e-2, # lambda
    rep(1e-2, dim_data), # daily
    rep(1e-2, dim_data), # weekly
    rep(1e-2, dim_data) # monthly
  ),
  upper = c(
    rep(15, dim_data), # sigma
    Inf, # lambda
    rep(1, dim_data), # daily
    rep(1, dim_data), # weekly
    rep(1, dim_data) # monthly
  ),
  eps = 1e-04,
  y = etf_train,
  har = c(5, 22),
  include_mean = TRUE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

```{r optimbvharllist}
class(bvhar_long_optim)
names(bvhar_long_optim)
```

Final fit:

```{r bvharlchoose}
bvhar_long_final <- bvhar_long_optim$fit
```


## Integrated Function

As mentioned, `choose_bvar()` and `choose_bvhar()` are still providing difficult ways of bounding methods.
So, there are another function: `choose_bayes()`.
You can set Empirical Bayes bound using `bound_bvhar(init_spec, lower_spec, upper_spec)`.

```{r boundemp}
# lower bound----------------
bvar_lower <- set_bvar(
  sigma = rep(1, dim_data),
  lambda = 1e-2,
  delta = rep(1e-2, dim_data)
)
# upper bound---------------
bvar_upper <- set_bvar(
  sigma = rep(15, dim_data),
  lambda = Inf,
  delta = rep(1, dim_data)
)
# bound--------------------
(bvar_bound <- bound_bvhar(
  init_spec = bvar_spec,
  lower_spec = bvar_lower,
  upper_spec = bvar_upper
))
```

```{r boundemplist}
class(bvar_bound)
names(bvar_bound)
```

Based on this `boundbvharemp`, we can use `choose_bayes()` function.
This function implements `choose_bvar()` or `choose_bvhar()` given inputs.

- `bayes_bound`: `boundbvharemp` object.
- `order`: `p` of BVAR or `har` of BVHAR.
- The other options are the same.

```{r bvaroptimother}
(bvar_optim_v2 <- choose_bayes(
  bayes_bound = bvar_bound,
  eps = 1e-04,
  y = etf_train,
  order = 3,
  include_mean = TRUE,
  parallel = list(cl = cl, forward = FALSE, loginfo = FALSE)
))
```

Do not forget shut down the cluster `cl`.

```{r stopparallel}
parallel::stopCluster(cl)
```
