---
title: "Cpp source usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cpp source usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r rmdsetup, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  out.width = "70%",
  fig.align = "center",
  fig.width = 6,
  fig.asp = .618
)
orig_opts <- options("digits")
options(digits = 3)
set.seed(1)
```

```{r setup}
library(bvhar)
```

# For Package Developers

This package provides public C++ headers. Some might be implement these useful.

- `ols`: OLS classes and structs
- `bayesfit`: Bayesian models classes and structs
- `forecast`: Forecast classes
- `spillover`: Spillover classes
- `utils`: Inline functions used in the headers

You can use these by writing in your R package DESCRIPTION:

```
LinkingTo: 
    BH,
    Rcpp,
    RcppEigen,
    bvhar
```

Also, you can use in your single `C++` source:

```
// [[Rcpp::depends(BH, RcppEigen, RcppSpdlog, RcppThread, bvhar)]]
// [[Rcpp::plugins(bvhar)]]
```

You need to add `plugins` attribute because the header in this package should define `USE_RCPP` macro.
Or you can use instead:

```{r, eval=FALSE}
Sys.setenv("PKG_CPPFLAGS" = "-DUSE_RCPP")
```

without using plugins attribute.

```{r resetopts, include=FALSE}
options(orig_opts)
```
