---
title: "Cpp source usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cpp source usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r rmdsetup, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  out.width = "70%",
  fig.align = "center",
  fig.width = 6,
  fig.asp = .618
)
orig_opts <- options("digits")
options(digits = 3)
set.seed(1)
```

```{r setup}
library(bvhar)
```

# For Package Developers

This package provides public C++ headers. Some might be implement these useful.

- `bvharsim.h`: Rcpp random generation functions that are widely used in Bayesian statistics.
- `ols.h`: OLS classes
- `minnesota.h`: Minnesota prior classes
- `mcmcsv.h`: Classes for stochastic volatility models. It includes
    - Minnesota prior
    - SSVS prior
    - Horseshoe prior
- `mcmchs.h`: Horseshoe prior classes
- `mcmcssvs.h`: SSVS prior classes
- `bvharprogress.h`: Simple progress bar classes
- `bvharinterrupt.h`: Interruption handler classes

You can use these by writing in your R package DESCRIPTION:

```
LinkingTo: 
    BH,
    Rcpp,
    RcppEigen,
    bvhar
```

Also, you can use in your single `C++` source:

```
// [[Rcpp::depends(BH, RcppEigen, bvhar)]]
```

## MCMC headers

`mcmc*.h` has classes that can conduct MCMC.
Since it is designed thread-safe, you can OpenMP for parallel multiple chain loop.

1. Initialize using smart pointer (in this package: `std::unique_ptr`)
    - Since each class requires other structure as its parameter, you first initialize it.
    - Each struct is inside the same header.
2. `doPosteriorDraws()` updates MCMC draws, so use this inside loop.
3. `returnRecords(burn, thin)` returns `Rcpp::List` of every MCMC record.

In case of SV model, you can define your own prior by defining a derived class.

```{r resetopts, include=FALSE}
options(orig_opts)
```
