---
title: "Minnesota Prior"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Minnesota Prior}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r rmdsetup, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  out.width = "70%",
  fig.align = "center",
  fig.width = 6,
  fig.asp = .618
)
orig_opts <- options("digits")
options(digits = 3)
set.seed(1)
```

```{r setup}
library(bvhar)
```

# Normal-inverse-Wishart Matrix

We provide functions to generate matrix-variate Normal and inverse-Wishart.

- `sim_mnormal(num_sim, mu, sig)`: `num_sim` of $\mathbf{X}_i \stackrel{iid}{\sim} N(\boldsymbol{\mu}, \Sigma)$.
- `sim_matgaussian(mat_mean, mat_scale_u, mat_scale_v)`: One $X_{m \times n} \sim MN(M_{m \times n}, U_{m \times m}, V_{n \times n})$ which means that $vec(X) \sim N(vec(M), V \otimes U)$.
- `sim_iw(mat_scale, shape)`: One $\Sigma \sim IW(\Psi, \nu)$.
- `sim_mniw(num_sim, mat_mean, mat_scale_u, mat_scale, shape)`: `num_sim` of $(X_i, \Sigma_i) \stackrel{iid}{\sim} MNIW(M, U, V, \nu)$.

Multivariate Normal generation gives `num_sim` x dim matrix.
For example, generating 3 vector from Normal($\boldsymbol{\mu} = \mathbf{0}_2$, $\Sigma = diag(\mathbf{1}_2)$):

```{r gennormal}
sim_mnormal(3, rep(0, 2), diag(2))
```

The output of `sim_matgaussian()` is a matrix.

```{r genmatnorm}
sim_matgaussian(matrix(1:20, nrow = 4), diag(4), diag(5))
```

When generating IW, violating $\nu > dim - 1$ gives error.
But we ignore $\nu > dim + 1$ (condition for mean existence) in this function.
Nonetheless, we recommend you to keep $\nu > dim + 1$ condition. As mentioned, it guarantees the existence of the mean.

```{r geniw}
sim_iw(diag(5), 7)
```

In case of `sim_mniw()`, it returns list with `mn` (stacked MN matrices) and `iw` (stacked IW matrices).
Each `mn` and `iw` has draw lists.

```{r genmniw}
sim_mniw(2, matrix(1:20, nrow = 4), diag(4), diag(5), 7)
```

<!-- Since each matrix is stacked rowwise, it is actually not that readable and practical. -->
This function has been defined for the next simulation functions.

# Minnesota Prior

## BVAR

Consider BVAR Minnesota prior setting,

$$A \sim MN(A_0, \Omega_0, \Sigma_e)$$

$$\Sigma_e \sim IW(S_0, \alpha_0)$$

- From Litterman (1986) and Bańbura et al. (2010)
- Each $A_0, \Omega_0, S_0, \alpha_0$ is defined by adding dummy observations
    - `build_xdummy()`
    - `build_ydummy()`

- `sigma`: Vector $\sigma_1, \ldots, \sigma_m$
    - $\Sigma_e = diag(\sigma_1^2, \ldots, \sigma_m^2)$
    - $\sigma_i^2 / \sigma_j^2$: different scale and variability of the data
- `lambda`
    - Controls the overall tightness of the prior distribution around the RW or WN
    - Governs the relative importance of the prior beliefs w.r.t. the information contained in the data
        - If $\lambda = 0$, then posterior = prior and the data do not influence the estimates.
        - If $\lambda = \infty$, then posterior expectations = OLS.
    - Choose in relation to the size of the system (Bańbura et al. (2010))
        - As `m` increases, $\lambda$ should be smaller to avoid overfitting (De Mol et al. (2008))
- `delta`: Persistence
    - Litterman (1986) originally sets high persistence $\delta_i = 1$
    - For Non-stationary variables: random walk prior $\delta_i = 1$
    - For stationary variables: white noise prior $\delta_i = 0$
- `eps`: Very small number to make matrix invertible

```{r minnesotaset}
bvar_lag <- 5
(spec_to_sim <- set_bvar(
  sigma = c(3.25, 11.1, 2.2, 6.8), # sigma vector
  lambda = .2, # lambda
  delta = rep(1, 4), # 4-dim delta vector
  eps = 1e-04 # very small number
))
```

- `sim_mncoef(p, bayes_spec, full = TRUE)` can generate both $A$ and $\Sigma$ matrices.
- In `bayes_spec`, only `set_bvar()` works.
- If `full = FALSE`, $\Sigma$ is not random. It is same as `diag(sigma)` from the `bayes_spec`.
- `full = TRUE` is the default.

```{r simminnesota}
(sim_mncoef(bvar_lag, spec_to_sim))
```

## BVHAR

`sim_mnvhar_coef(bayes_spec, full = TRUE)` generates BVHAR model setting:

$$\Phi \mid \Sigma_e \sim MN(M_0, \Omega_0, \Sigma_e)$$

$$\Sigma_e \sim IW(\Psi_0, \nu_0)$$

- similar to BVAR, `bayes_spec` option wants `bvharspec`. But
    - `set_bvhar()`
    - `set_weight_bvhar()`
- There is `full = TRUE`, too.

### BVHAR-S

```{r bvharvarset}
(bvhar_var_spec <- set_bvhar(
  sigma = c(1.2, 2.3), # sigma vector
  lambda = .2, # lambda
  delta = c(.3, 1), # 2-dim delta vector
  eps = 1e-04 # very small number
))
```

```{r simbvhars}
(sim_mnvhar_coef(bvhar_var_spec))
```

### BVHAR-L

```{r bvharvharset}
(bvhar_vhar_spec <- set_weight_bvhar(
  sigma = c(1.2, 2.3), # sigma vector
  lambda = .2, # lambda
  eps = 1e-04, # very small number
  daily = c(.5, 1), # 2-dim daily weight vector
  weekly = c(.2, .3), # 2-dim weekly weight vector
  monthly = c(.1, .1) # 2-dim monthly weight vector
))
```

```{r simbvharl}
(sim_mnvhar_coef(bvhar_vhar_spec))
```

```{r resetopts, include=FALSE}
options(orig_opts)
```
