---
title: "Shrinkage Priors"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Shrinkage Priors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r rmdsetup, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  out.width = "70%",
  fig.align = "center",
  fig.width = 6,
  fig.asp = .618
)
orig_opts <- options("digits")
options(digits = 3)
set.seed(1)
```

```{r setup}
library(bvhar)
```

```{r etfdat}
etf <- etf_vix[1:100, 1:3]
# Split-------------------------------
h <- 5
etf_eval <- divide_ts(etf, h)
etf_train <- etf_eval$train
etf_test <- etf_eval$test
```


# Stochastic Search Variable Selection (SSVS) Prior

- `y`: Multivariate time series data. It should be data frame or matrix, which means that every column is numeric. Each column indicates variable, i.e. it sould be wide format.
- `har`: Order of VHAR
- `num_chains`: Number of chains
    - If OpenMP is enabled, parallel loop will be run.
- `num_iter`: Total number of iterations
- `num_burn`: Number of burn-in
- `thinning`: Thinning
- `bayes_spec`: Output of `set_ssvs()`
    - By default, use a default semi-automatic approach using `choose_ssvs()`.
- `init_spec`: Gibbs sampler initialization by `init_ssvs()`.
  - By default, `init_ssvs(type = "auto")` uses OLS.
- `include_mean = TRUE`: By default, you include the constant term in the model.
- `minnesota = c("no", "short", "longrun")`: Minnesota-type shrinkage.
- `verbose = FALSE`: Progress bar
- `num_thread`: Number of thread for OpenMP
    - Used in both Eigen computation and parallel multi-chain loop
    - This option is valid only when OpenMP in user's machine.

```{r fitssvs}
(fit_ssvs <- bvhar_ssvs(etf_train, num_chains = 1, num_iter = 50, include_mean = FALSE, minnesota = "longrun"))
```

`autoplot()` for the fit (`bvharsp` object) provides coefficients heatmap.
There is `type` argument, and the default `type = "coef"` draws the heatmap.

```{r heatssvs}
autoplot(fit_ssvs)
```


# Horseshoe Prior

`bayes_spec` is the initial specification by `set_horseshoe()`. Others are the same.

```{r fiths}
(fit_hs <- bvhar_horseshoe(etf_train, num_chains = 2, num_iter = 50, include_mean = FALSE, minnesota = "longrun"))
```

```{r heaths}
autoplot(fit_hs)
```


# Models with Stochastic Volatilities

`bvhar_sv()` fits VHAR-SV with shrinkage priors.

- Three different prior for covariance, and specify through `bayes_spec`
- `sv_spec`: prior settings for SV, `set_sv()`

## SSVS

```{r svssvs}
(fit_ssvs_sv <- bvhar_sv(etf_train, num_chains = 2, num_iter = 50, bayes_spec = set_ssvs(), sv_spec = set_sv(), include_mean = FALSE, minnesota = "longrun"))
```

```{r heatssvssv}
autoplot(fit_ssvs_sv)
```

## Horseshoe

```{r}
(fit_hs_sv <- bvhar_sv(etf_train, num_chains = 2, num_iter = 50, bayes_spec = set_horseshoe(), sv_spec = set_sv(), include_mean = FALSE, minnesota = "longrun"))
```

## Bayesian visualization

`autoplot()` also provides Bayesian visualization. `type = "trace"` gives MCMC trace plot.

```{r}
autoplot(fit_hs_sv, type = "trace", regex_pars = "tau")
```

`type = "dens"` draws MCMC density plot.

```{r denshs}
autoplot(fit_hs, type = "dens", regex_pars = "tau")
```


```{r resetopts, include=FALSE}
options(orig_opts)
```
